Temporal semantics for a live coding language

### 2014-05-08 paper/paper.tex
started on overrun text

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\mathbf{data}\;\Conid{Warning}\mathrel{=}\Conid{StrongOverrun}\;\Conid{VTime}\mid \Conid{WeakOverrun}\;\Conid{VTime}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\mathbf{data}\;\Conid{TemporalE}\;\Varid{a}\mathrel{=}\Conid{TE}\;(\Conid{VTime}\to \Conid{Temporal}\;(\Varid{a},[\mskip1.5mu \Conid{Warning}\mskip1.5mu])){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\mathbf{instance}\;\Conid{Monad}\;\Conid{TemporalE}\;\mathbf{where}{}\<[E]%
\\
\>[B]{}\hsindent{5}{}\<[5]%
\>[5]{}\Varid{return}\;\Varid{a}\mathrel{=}\Conid{TE}\;(\mathbin{\char92 \char95 }\to \Varid{return}\;(\Varid{a},[\mskip1.5mu \mskip1.5mu])){}\<[E]%
\\
\>[B]{}\hsindent{5}{}\<[5]%
\>[5]{}(\Conid{TE}\;\Varid{p})\bind \Varid{q}\mathrel{=}\Conid{TE}\;(\lambda \Varid{eps}\to \mathbf{do}\;(\Varid{a},\Varid{es})\leftarrow \Varid{p}\;\Varid{eps}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}\mathbf{let}\;(\Conid{TE}\;\Varid{q'})\mathrel{=}\Varid{q}\;\Varid{a}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}(\Varid{b},\Varid{es'})\leftarrow \Varid{q'}\;\Varid{eps}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}\Varid{return}\;(\Varid{b},\Varid{es}\plus \Varid{es'})){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

>>>>

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\mathbf{data}\;\Conid{Warning}\mathrel{=}\Conid{Strong}\;\Conid{VTime}\mid \Conid{Weak}\;\Conid{VTime}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\mathbf{data}\;\Conid{TemporalE}\;\Varid{a}\mathrel{=}{}\<[E]%
\\
\>[B]{}\hsindent{5}{}\<[5]%
\>[5]{}\Conid{TE}\;(\Conid{VTime}\to \Conid{Temporal}\;(\Varid{a},[\mskip1.5mu \Conid{Warning}\mskip1.5mu])){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\mathbf{instance}\;\Conid{Monad}\;\Conid{TemporalE}\;\mathbf{where}{}\<[E]%
\\
\>[B]{}\hsindent{5}{}\<[5]%
\>[5]{}\Varid{return}\;\Varid{a}\mathrel{=}\Conid{TE}\;(\mathbin{\char92 \char95 }\to \Varid{return}\;(\Varid{a},[\mskip1.5mu \mskip1.5mu])){}\<[E]%
\\
\>[B]{}\hsindent{5}{}\<[5]%
\>[5]{}(\Conid{TE}\;\Varid{p})\bind \Varid{q}\mathrel{=}\Conid{TE}\;(\lambda \Varid{eps}\to \mathbf{do}\;(\Varid{a},\Varid{es})\leftarrow \Varid{p}\;\Varid{eps}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}\mathbf{let}\;(\Conid{TE}\;\Varid{q'})\mathrel{=}\Varid{q}\;\Varid{a}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}(\Varid{b},\Varid{es'})\leftarrow \Varid{q'}\;\Varid{eps}{}\<[E]%
\\
\>[5]{}\hsindent{30}{}\<[35]%
\>[35]{}\Varid{return}\;(\Varid{b},\Varid{es}\plus \Varid{es'})){}\<[E]%
\ColumnHook
\end{hscode}\resethooks
